---
title: "Untitled"
author: "Rebecca Silva"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# data
```{r}
data_cv = data %>% mutate(
  five_stars_cat = ifelse(five_stars == "1","yes", "no" ), 
  five_stars_cat = as.factor(five_stars_cat))

set.seed(1)
row_train_kernel <- createDataPartition(y = data_cv$five_stars_cat,
                                p = .4,
                                list = FALSE)
```


# Linear Kernal 

```{r}
ctrl <- trainControl(method = "cv") 

set.seed(1)
svml.fit <- train(five_stars_cat ~ neighbourhood_group + room_type+ price + number_of_reviews + reviews_per_month  + availability_365,
                   data = data_cv, 
                   subset = row_train_kernel,
                  method = "svmLinear2",
                  preProcess = c("center", "scale"),
                  tuneGrid = data.frame(cost = exp(seq(-5,1,len=30))),
                  trControl = ctrl)

ggplot(svml.fit, highlight = TRUE)


### try TUNE 
library(e1071)
set.seed(1)
linear.tune <- tune.svm(five_stars_cat ~ neighbourhood_group + room_type+ price + number_of_reviews + reviews_per_month  + availability_365, 
                        data = data_cv[row_train,], 
                        kernel = "linear", 
                        cost = exp(seq(-5,0,len=20)))
summary(linear.tune)
```

Train performance:
```{r}
pred.linear <- predict(svml.fit, newdata = data_cv[row_train_kernel,])# prediction is a class label 

confusionMatrix(data = pred.linear, 
                reference = data_cv$five_stars_cat[row_train])
```

The accurary is 0.8312 and Kappa value is 0.6448, meaning the model correctly intentifies the purchase brand for 83% of the predictions, and 65% after taking account of correctly identifying by chance. 

Test performance: 
```{r}
pred.linear.test <- predict(svml.fit, newdata = OJ[-row_train,])


confusionMatrix(data = pred.linear.test, 
                reference = OJ$Purchase[-row_train])
```

The accurary is 0.833 and Kappa value is 0.6448, which is very similar to the training error rate. 


## b)
```{r}
svmr.grid <- expand.grid(C = exp(seq(-1,4,len=10)),
                         sigma = exp(seq(-6,-2,len=10)))
library(kernlab)
set.seed(1)             
svmr.fit <- train(five_stars_cat ~  lat+ long+ room_type+ price + number_of_reviews + reviews_per_month  + availability_365,
                  data = data_cv, 
                  subset = row_train_cv,
                  method = "svmRadial",
                  preProcess = c("center", "scale"),
                  tuneGrid = svmr.grid,
                  trControl = ctrl)

ggplot(svmr.fit, highlight = TRUE)
```

```{r}
pred.radial <- predict(svmr.fit, newdata = data_cv[row_train,])# prediction is a class label 

confusionMatrix(data = pred.radial, 
                reference = data_cv$five_stars_cat[row_train])
```
Train performance:

The accurary is 0.8512 and Kappa value is 0.68, meaning the model correctly intentifies the purchase brand for 85% of the predictions, and 68% after taking account of correctly identifying by chance.

Test performance: 
```{r}
pred.radial.test <- predict(svmr.fit, newdata = OJ[-row_train,])


confusionMatrix(data = pred.radial.test, 
                reference = OJ$Purchase[-row_train])
```
Test performance: 

The accurary is 0.814 and Kappa value is 0.59.

Conclusion: 
I would choose radial svm to predict OJ brand because it produces a model with the best training performance. 
